Penalized linear mixed models for structured genetic data

### 2021-02-21 main.tex
First pass with genome-wide analysis results. Trying different dimensions on cluster.

%------------------------------%
\subsection{\anna{Genomewide analysis case study}}
%------------------------------%

@@

>>>>

%------------------------------%
\subsection{\anna{Genomewide analysis}}
%------------------------------%

@@

%------------------------------%
\subsection{\anna{Genome-wide analysis case study}}
%------------------------------%

\begin{figure}[hbt]
\centering
\includegraphics[scale = 0.9]{figures/genomewide_prc.png}
\caption{Precision recall curves across all $\lambda$ values from the Empirical genome-wide analysis. Single replication, $\eta = 0.5, \xi = 0.8$.}
\label{fig:gw_prc}
\end{figure}

\begin{figure}[hbt]
\centering
\includegraphics[scale = 0.9]{figures/genomewide_pop_inf_snps.png}
\caption{Absolute correlation of selected, non-causal SNPs with the first principal component of the data in Empirical genome-wide analysis. Selection is calculated across all $\lambda$ values for a single replication. $\eta = 0.5, \xi = 0.8$.}
\label{fig:gw_pop_inf}
\end{figure}
